wgcna

### 2019-09-03 analysis/08_wgcna.Rmd
now with just pit, also, new factor variable

# WGCNA analysis, first pass

@@

## All characterization data

```{r wgcna, message=FALSE, warning=FALSE, cache=TRUE}

subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary",
                           "male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Characterization dendrogram with trait heatmap")

**Fig 1. Characterization dendrogram with trait heatmap.**. 
 Most hypothalamus and pituitary samples separte form the gonad samples, but some are clusters contain samples from all tissues.

@@

```{r wgcna-pit, message=FALSE, warning=FALSE, cache=TRUE}

subsetWGCNA(c("female.pitutary", "male.pitutary"),
            mytitle = "Pituitary dendrogram with trait heatmap")
```

>>>>

# WGCNA analysis, second pass

@@

@@

```{r wgcna-pit, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("F.pit", "M.pit"), 2000000, "Pituitary dendrogram with trait heatmap")
```
